KidsAIR: Main analysis initial steps

### 2020-11-18 main_analysis_initial.Rmd
major analysis updates

kids_kw_report_1obs <- read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  group_by(home) %>% 
  mutate(mean_kw_per_exp = mean(kw_perc_expected, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  mutate(kw_perc_exp_cat = cut(kw_perc_expected, 
                               breaks = c(0, 42, 83, 129, 50000),
                               labels = c("Q1", "Q2", "Q3", "Q4"))) %>% 
  dplyr::select(-home_winter_id, -treatment_assigned, -treatment_actual, -home_id)

kids_kw_report_2obs <- read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  group_by(area, home_winter_id) %>% 
  mutate(mean_kw_per_exp = mean(kw_perc_expected, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(area, home_winter_id, .keep_all = TRUE) %>% 
  mutate(kw_perc_exp_cat = cut(kw_perc_expected, 
                               breaks = c(0, 37, 74, 118, 50000),
                               labels = c("Q1", "Q2", "Q3", "Q4"))) %>% 
  dplyr::select(-home_winter_id, -treatment_assigned, -treatment_actual, -home_id)

# Condense LRTI data to 1 obs per child/winter and select analysis vars
lrti_1obs_per_winter <- read_rds(paste0(file_path, "Output/lrti_final_data.rds")) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  mutate(cohort = round_date(csq_date, unit = "year")) %>% 
  separate(cohort, c("cohort", "trash"), sep = "-") %>% 
  group_by(area, child_id_num, winter_id) %>% 
  mutate(lrti_events_winter = n(),
         lrti_events_winter = as.numeric(lrti_events_winter),
         lrti_events_winter = if_else(is.na(person_time_lrti), 0, lrti_events_winter),
         person_time_lrti_winter = sum(person_time_lrti),
         person_time_no_lrti_winter = as.numeric(person_time_possible - person_time_lrti_winter),
         person_time_no_lrti_winter = if_else(is.na(person_time_no_lrti_winter), person_time_possible,
                                             person_time_no_lrti_winter),
         person_time_at_risk_winter = as.numeric(person_time_no_lrti_winter)/7,
         lrti_incidence_winter = lrti_events_winter/person_time_at_risk_winter,
         lrti_incidence_winter = if_else(is.na(lrti_incidence_winter), 0, lrti_incidence_winter)) %>% 
  arrange(area, home, child_id_num, winter_id) %>%
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, winter_id, 
                lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter)

# Condense LRTI data to 1 obs per child and select analysis vars
lrti_1obs_total <- read_rds(paste0(file_path, "Output/lrti_final_data.rds")) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  mutate(cohort = round_date(csq_date, unit = "year")) %>% 
  separate(cohort, c("cohort", "trash"), sep = "-") %>% 
  group_by(area, child_id_num, winter_id) %>% 
  mutate(lrti_events = n()) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  group_by(area, child_id_num) %>% 
  mutate(lrti_events = as.numeric(lrti_events),
         lrti_events = if_else(is.na(person_time_no_lrti_total), 0, lrti_events),
         lrti_events_total = sum(lrti_events, na.rm = TRUE),
         person_time_no_lrti_total = as.numeric(person_time_no_lrti_total),
         person_time_no_lrti_total = if_else(is.na(person_time_no_lrti_total), person_time_possible,
                                             person_time_no_lrti_total),
         person_time_at_risk_total = sum(person_time_no_lrti_total, na.rm = TRUE),
         person_time_at_risk_total = as.numeric(person_time_at_risk_total)/7,
         lrti_incidence_total = lrti_events_total/person_time_at_risk_total,
         lrti_incidence_total = if_else(is.na(lrti_incidence_total), 0, lrti_incidence_total)) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  left_join(kids_amb_pm_data, by = c("area", "home")) %>% 
  mutate(pm_filter = if_else(sample_date >= person_time_start & sample_date <= person_time_end, 1, 0)) %>% 
  filter(pm_filter == 1) %>% 
  group_by(area, child_id_num) %>% 
  mutate(amb_pm_lrti = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, lrti_events_total, person_time_at_risk_total, lrti_incidence_total,
         amb_pm_lrti, person_time_start, person_time_end, home_winter_id, winter_id) %>% 
  left_join(kids_amb_temp_data, by = c("area", "home")) %>% 
  mutate(temp_filter = if_else(sample_date >= person_time_start & sample_date <= person_time_end, 1, 0)) %>% 
  filter(temp_filter == 1 | child_id_num == 94) %>% 
  group_by(area, child_id_num) %>% 
  mutate(amb_temp_lrti = mean(mean_temp, na.rm = TRUE),
         amb_temp_lrti = if_else(child_id_num == 94, NaN, amb_temp_lrti),
         amb_dewp_lrti = mean(mean_dewp, na.rm = TRUE),
         amb_dewp_lrti = if_else(child_id_num == 94, NaN, amb_dewp_lrti),
         amb_pressure_lrti = mean(mean_pressure, na.rm = TRUE),
         amb_pressure_lrti = if_else(child_id_num == 94, NaN, amb_pressure_lrti),
         amb_wind_lrti = mean(mean_wind_knots, na.rm = TRUE),
         amb_wind_lrti = if_else(child_id_num == 94, NaN, amb_wind_lrti)) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, winter_id,
                lrti_events_total, person_time_at_risk_total, lrti_incidence_total,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, lrti_events_total, person_time_at_risk_total, lrti_incidence_total,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti)

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_kw_report_1obs, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, mean_kw_per_exp, kw_perc_exp_cat) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         filter_type2 = as.character(filter_type),
         filter_type2 = if_else(treatment_assigned == "Education", "Ed Home", filter_type2),
         filter_type2 = factor(filter_type2,
                              levels = c("Honeywell", "Large Filtrete", "Small Filtrete",
                                         "Winix", "Ed Home")),
         kw_perc_exp_cat2 = as.character(kw_perc_exp_cat),
         kw_perc_exp_cat2 = if_else(treatment_assigned == "Education", "Ed Home", kw_perc_exp_cat2),
         kw_perc_exp_cat2 = factor(kw_perc_exp_cat2,
                                  levels = c("Q1", "Q2", "Q3", "Q4", "Ed Home"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_kw_report_1obs, by = c("area", "home", "winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, mean_kw_per_exp, kw_perc_exp_cat) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         filter_type2 = as.character(filter_type),
         filter_type2 = if_else(treatment_assigned == "Education", "Ed Home", filter_type2),
         filter_type2 = factor(filter_type2,
                              levels = c("Honeywell", "Large Filtrete", "Small Filtrete",
                                         "Winix", "Ed Home")),
         kw_perc_exp_cat2 = as.character(kw_perc_exp_cat),
         kw_perc_exp_cat2 = if_else(treatment_assigned == "Education", "Ed Home", kw_perc_exp_cat2),
         kw_perc_exp_cat2 = factor(kw_perc_exp_cat2,
                                  levels = c("Q1", "Q2", "Q3", "Q4", "Ed Home"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

>>>>

kids_kw_report_1obs <- read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  group_by(home) %>% 
  mutate(mean_kw_per_exp = mean(kw_perc_expected, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  mutate(kw_perc_exp_cat = cut(kw_perc_expected, 
                               breaks = c(0, 30, 56, 106, 1000),
                               labels = c("Q1", "Q2", "Q3", "Q4"))) %>% 
  dplyr::select(-home_winter_id, -treatment_assigned, -treatment_actual, -home_id)

kids_kw_report_2obs <- read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  group_by(area, home_winter_id) %>% 
  mutate(mean_kw_per_exp = mean(kw_perc_expected, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(area, home_winter_id, .keep_all = TRUE) %>% 
  mutate(kw_perc_exp_cat = cut(kw_perc_expected, 
                               breaks = c(0, 29, 53, 96, 1000),
                               labels = c("Q1", "Q2", "Q3", "Q4"))) %>% 
  dplyr::select(-home_winter_id, -treatment_assigned, -treatment_actual, -home_id)

# Condense LRTI data to 1 obs per child/winter and select analysis vars
lrti_1obs_per_winter <- read_rds(paste0(file_path, "Output/lrti_final_data.rds")) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  mutate(cohort = round_date(csq_date, unit = "year")) %>% 
  separate(cohort, c("cohort", "trash"), sep = "-") %>% 
  group_by(area, child_id_num, winter_id) %>% 
  mutate(lrti_events_winter = n(),
         lrti_events_winter = as.numeric(lrti_events_winter),
         lrti_events_winter = if_else(is.na(person_time_lrti), 0, lrti_events_winter),
         person_time_lrti_winter = sum(person_time_lrti),
         person_time_no_lrti_winter = as.numeric(person_time_possible - person_time_lrti_winter),
         person_time_no_lrti_winter = if_else(is.na(person_time_no_lrti_winter), person_time_possible,
                                             person_time_no_lrti_winter),
         person_time_at_risk_winter = as.numeric(person_time_no_lrti_winter)/7,
         lrti_incidence_winter = lrti_events_winter/person_time_at_risk_winter,
         lrti_incidence_winter = if_else(is.na(lrti_incidence_winter), 0, lrti_incidence_winter)) %>% 
  arrange(area, home, child_id_num, winter_id) %>%
  left_join(kids_amb_pm_data, by = c("area", "home")) %>% 
  mutate(pm_filter = if_else((sample_date >= person_time_start) & (sample_date <= person_time_end), 1, 0)) %>% 
  filter(pm_filter == 1) %>% 
  group_by(area, child_id_num, winter_id) %>% 
  mutate(amb_pm_lrti = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter,
         amb_pm_lrti, person_time_start, person_time_end, home_winter_id, winter_id) %>% 
  left_join(kids_amb_temp_data, by = c("area", "home")) %>% 
  mutate(temp_filter = if_else((sample_date >= person_time_start) & (sample_date <= person_time_end), 1, 0)) %>% 
  filter(temp_filter == 1 | child_id_num == 94) %>% 
  group_by(area, child_id_num, winter_id) %>% 
  mutate(amb_temp_lrti = mean(mean_temp, na.rm = TRUE),
         amb_temp_lrti = if_else(child_id_num == 94, NaN, amb_temp_lrti),
         amb_dewp_lrti = mean(mean_dewp, na.rm = TRUE),
         amb_dewp_lrti = if_else(child_id_num == 94, NaN, amb_dewp_lrti),
         amb_pressure_lrti = mean(mean_pressure, na.rm = TRUE),
         amb_pressure_lrti = if_else(child_id_num == 94, NaN, amb_pressure_lrti),
         amb_wind_lrti = mean(mean_wind_knots, na.rm = TRUE),
         amb_wind_lrti = if_else(child_id_num == 94, NaN, amb_wind_lrti)) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, winter_id,
                lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  ungroup()

# Condense LRTI data to 1 obs per child and select analysis vars
lrti_1obs_total <- read_rds(paste0(file_path, "Output/lrti_final_data.rds")) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  mutate(cohort = round_date(csq_date, unit = "year")) %>% 
  separate(cohort, c("cohort", "trash"), sep = "-") %>% 
  group_by(area, child_id_num, winter_id) %>% 
  mutate(lrti_events = n()) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  group_by(area, child_id_num) %>% 
  mutate(lrti_events = as.numeric(lrti_events),
         lrti_events = if_else(is.na(person_time_no_lrti_total), 0, lrti_events),
         lrti_events_total = sum(lrti_events, na.rm = TRUE),
         person_time_no_lrti_total = as.numeric(person_time_no_lrti_total),
         person_time_no_lrti_total = if_else(is.na(person_time_no_lrti_total), person_time_possible,
                                             person_time_no_lrti_total),
         person_time_at_risk_total = sum(person_time_no_lrti_total, na.rm = TRUE),
         person_time_at_risk_total = as.numeric(person_time_at_risk_total)/7,
         lrti_incidence_total = lrti_events_total/person_time_at_risk_total,
         lrti_incidence_total = if_else(is.na(lrti_incidence_total), 0, lrti_incidence_total)) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  left_join(kids_amb_pm_data, by = c("area", "home")) %>% 
  mutate(pm_filter = if_else((sample_date >= person_time_start) & (sample_date <= person_time_end), 1, 0)) %>% 
  filter(pm_filter == 1) %>% 
  group_by(area, child_id_num) %>% 
  mutate(amb_pm_lrti = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, lrti_events_total, person_time_at_risk_total, lrti_incidence_total,
         amb_pm_lrti, person_time_start, person_time_end, home_winter_id, winter_id) %>% 
  left_join(kids_amb_temp_data, by = c("area", "home")) %>% 
  mutate(temp_filter = if_else((sample_date >= person_time_start) & (sample_date <= person_time_end), 1, 0)) %>% 
  filter(temp_filter == 1 | child_id_num == 94) %>% 
  group_by(area, child_id_num) %>% 
  mutate(amb_temp_lrti = mean(mean_temp, na.rm = TRUE),
         amb_temp_lrti = if_else(child_id_num == 94, NaN, amb_temp_lrti),
         amb_dewp_lrti = mean(mean_dewp, na.rm = TRUE),
         amb_dewp_lrti = if_else(child_id_num == 94, NaN, amb_dewp_lrti),
         amb_pressure_lrti = mean(mean_pressure, na.rm = TRUE),
         amb_pressure_lrti = if_else(child_id_num == 94, NaN, amb_pressure_lrti),
         amb_wind_lrti = mean(mean_wind_knots, na.rm = TRUE),
         amb_wind_lrti = if_else(child_id_num == 94, NaN, amb_wind_lrti)) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, winter_id,
                lrti_events_total, person_time_at_risk_total, lrti_incidence_total,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  ungroup() %>% 
  dplyr::select(area, home, cohort, child_id_num, lrti_events_total, person_time_at_risk_total, lrti_incidence_total,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti)

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_kw_report_1obs, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, mean_kw_per_exp, kw_perc_exp_cat) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         kw_perc_exp_cat2 = as.character(kw_perc_exp_cat),
         kw_perc_exp_cat2 = if_else(treatment_assigned == "Filter", kw_perc_exp_cat2, treatment_assigned),
         kw_perc_exp_cat2 = factor(kw_perc_exp_cat2,
                                  levels = c("Placebo", "Education", "Q1", "Q2", "Q3", "Q4"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_kw_report_1obs, by = c("area", "home", "winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, 
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, mean_kw_per_exp, kw_perc_exp_cat) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         kw_perc_exp_cat2 = as.character(kw_perc_exp_cat),
         kw_perc_exp_cat2 = if_else(treatment_assigned == "Filter", kw_perc_exp_cat2, treatment_assigned),
         kw_perc_exp_cat2 = factor(kw_perc_exp_cat2,
                                  levels = c("Placebo", "Education", "Q1", "Q2", "Q3", "Q4"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))
